---
title: "Vader, but on R"
author: "Jakob Woerner"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: 'united'
    highlight: 'tango'
    toc: yes
    toc_float: true
    code_folding: 'show'
    df_print: 'paged'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment = NA)
```

# Setup
```{r, warning=FALSE, message=FALSE}
library(vader);library(xlsx);library(tidyverse)
```

# Goal

Run cleaning and then Vader sentiment analysis, but using R.


# Load Data

```{r, warning=TRUE, message=FALSE}
vaccine_college_500 <- read_csv("data/vaccine_college_500.csv")
vaccine_college_500_2 <- read_csv("data/vaccine_college_500_2.csv")
```

# Clean Data

```{r}
vc <- bind_rows(vaccine_college_500, vaccine_college_500_2)
```


Remove first 'b'

```{r}
vc1 <- vc %>% 
  mutate(clean_text = str_sub(text, 2)) %>% 
  select(clean_text, everything())
```

Remove URLs and newline characters

```{r}
vc2 <- vc1 %>% 
  mutate(clean_text = gsub("http.*","",  clean_text)) %>% 
  mutate(clean_text = gsub("https.*","",  clean_text)) %>% 
  mutate(clean_text = gsub("\\\\n","",  clean_text))
```

Let's not make lowercase or remove special characters, since those might be used in the vader algorithm.

Remove @, quotation marks, and apostraphes

```{r}
vc2$clean_text <- gsub("'", '', vc2$clean_text)
vc2$clean_text <- gsub('"', '', vc2$clean_text)
vc2$clean_text <- gsub("@\\w+", "", vc2$clean_text)
```

Remove duplicates

```{r}
vc3 <- vc2[!duplicated(vc2$clean_text),]
```

# Apply vader    

```{r}
t1 <- Sys.time()
vader_result <- vader_df(vc3$clean_text) 
t2 <- t1 - Sys.time()
```
About 7 minutes


No neutral words

```{r}
# Creates Error
# vader_result_2 <- vader_df(vc3$clean_text[1:10], neu_set = TRUE) 
```

# Save Data

```{r}
write.csv(vc3, "sentiment_clean_college_data.csv")
write.csv(vader_result, "vader_result_R.csv")
# write.csv(vader_result_2, "vader_no_neutral_R.csv")
```

# Neutralize

Recode to remove the neutral category. I will also remove the "Pin Code:[411041]" tweets

```{r}
vader_no_neutral <- vader_result %>% 
  filter(!str_detect(text, "Pin Code|Pincode")) %>% 
  drop_na() %>% # redundant
  mutate(positive = pos / (pos + neg),
         negative = neg / (pos + neg),
         neutral = if_else(neu == 1, 1, 0),
         assigned = if_else(neu == 1, "Neutral",
                            if_else(positive > 0.5, "Positive","Negative")))

write.csv(vader_no_neutral, "vader_no_nuetral_R.csv")
```

# Save sample

```{r}
set.seed(2021)
vader_sample <- vader_no_neutral %>% 
  select(text, positive, negative, assigned) %>%
  drop_na() %>% 
  sample_n(500)
  
write.xlsx(vader_sample, file = "data/vader_sample.xlsx",row.names = FALSE)
```




# Session Information
```{r}
sessioninfo::session_info()
```


